Site location study for a high-mountain millimeter observatory in the Colombian Andes I: In situ data

### 2017-04-22 pasp/paperclimate.tex
geoclustering

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{slist.pdf}
\includegraphics[scale=0.5]{slistz.pdf}
\caption{Map of stations in our final shortlist. The highlighted region on (a) is seen in more detail in (b), which corresponds approximately to the Colombian \emph{altiplano} region. Marker size is proportional to the quality index $Q_j$, where the largest points correspond to a $Q_j=10$.}\label{shortlist}
\end{center}
\end{figure}

@@

All stations outside of the region located within the latitude, longitude range $[(4.3,6.2),(-72.4,-74.5)]$ seem to be outliers, and while they could indicate unusually dry, sunny regions, there are not enough stations nearby to say anything conclusively. Furthermore, those stations only measured one or two variables, which leads us to reject them from our shortlist. \\

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{slist.pdf}
\includegraphics[scale=0.5]{slistz.pdf}
\caption{Map of stations in our final shortlist. The highlighted region on (a) is seen in more detail in (b), which corresponds approximately to the Colombian \emph{altiplano} region. Marker size is proportional to the probability $P_j$, where the largest points correspond to a $Q_j=10$.}\label{shortlist}
\end{center}
\end{figure}

@@

All stations outside of the region located within the latitude, longitude range $[(4.3,6.2),(-72.4,-74.5)]$ seem to be outliers, and while they could indicate unusually dry, sunny regions, there are not enough stations nearby to say anything conclusively as can be seen in Figure \ref{outliers}. Furthermore, those stations only measured precipitation ($Q_j=2.2$), which leads us to reject them from our shortlist. \\
%The points of interest outside this region are too sparsely located to suggest a candidate region of interest, \\

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.55]{outliers.pdf}
\caption{Map of stations in our final shortlist but outside of the Colombian \emph{altiplano} region highlighted in Figure \ref{shortlist}. Marker size is proportional to the Probability $P_j$, where the smallest points correspond to a $Q_j=2.2$.}\label{outliers}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.55]{geobic.pdf}
\includegraphics[scale=0.55]{geobic2.pdf}
\caption{Results  for a lowest-BIC spherical covariance Gaussian Mixture Model geographical clustering on the stations located inside the red circle in Figure \ref{shortlist}b. (a) BIC results for different number of clusters. (b) Lowest-BIC GMM geographical clustering classification.}\label{geobic}
\end{center}
\end{figure}
